SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/paper.tex
Reset Michaela's affiliation, added acknowledgements.

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert, apalmer, regneri\}} \\
{\tt @coli.uni-saarland.de} \\
}
\date{}

@@

>>>>

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer, and Michaela Regneri \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert, apalmer, regneri\}} \\
{\tt @coli.uni-saarland.de}}

\date{}

@@

\section*{Acknowledgements}
We thank the three anonymous reviewers for their helpful comments. This research was supported in part by the Cluster of Excellence "Multi-modal Computing and Interaction" in the German Excellence Initiative.
